Predator summary

### 2023-01-25 reports/01_predators.qmd
Begin predator sighting map

tar_load("predators_agg", store = here::here("_targets"))
```

# South Georgia winter predators

## Counts

@@

>>>>

tar_load(c("predators_agg", "sg_sf"), store = here::here("_targets"))
source(here::here("R", "sp.R"))
```

## South Georgia winter predators

### Counts

@@

### Maps

```{r}
#| label: predator_map

predators_sf <- predators_agg %>% 
  semi_join(top_six, by = "species") %>% 
  filter(year == 2016) %>% 
  sf::st_as_sf(coords = c("lon_mean", "lat_mean"), 
               crs = sp::CRS("+proj=longlat +datum=WGS84"))

map_lim <- sf::st_bbox(predators_sf) %>% 
  sf::st_as_sfc(crs = "EPSG:4326") %>% 
  sf::st_transform(sg_proj()) %>% 
  sf::st_bbox()

ggplot() +
  geom_sf(data = sg_sf) +
  geom_sf(aes(color = count), data = predators_sf) +
  scale_color_gradient(low = "lightblue", high = "darkred",
                       limits = c(0, 1000)) +
  facet_wrap(~species) +
  coord_sf(xlim = map_lim[c("xmin", "xmax")] + c(-1e5, 1e5),
           ylim = map_lim[c("ymin", "ymax")] + c(-1e5, 1e5),
           expand = FALSE,
           crs = sg_proj()) +
  theme_minimal()

```
